<span style='line-height:60px; font-size:60px'>Changing communicative need<br>predicts lexical competition<br>and contributes<br>to language change</span></font>

### 2019-11-20 ruse2019/index.Rmd
news

---
title: "<span style='line-height:60px; font-size:60px'>Changing communicative need<br>predicts lexical competition<br>and contributes<br>to language change</span></font>"
author: "<font size=6>Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith<br></font><font size=5>Centre for Language Evolution, University of Edinburgh</font>"
date: "<font size=5>RUSE Symposium, Manchester, August 2019</font>"
output:
  xaringan::moon_reader:
    css: img/xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: false
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false
---
class: inverse
# All languages change

@@

<div style="font-size:10pt; line-height:20px">
Karjus, A., Blythe, R.A., Kirby, S., Smith, K., [to appear in Language Dynamics and Change]. Quantifying the dynamics of topical fluctuations in language.<br>
Regier, T., Carstensen, A., Kemp, C., 2016. Languages Support Efficient Communication about the Environment: Words for Snow Revisited. PLOS ONE 11, 1–17.<br>
Gibson, E., Futrell, R., Jara-Ettinger, J., Mahowald, K., Bergen, L., Ratnasingam, S., Gibson, M., Piantadosi, S.T., Conway, B.R., 2017. Color naming across languages reflects color use. Proceedings of the National Academy of Sciences. <br>
Hamilton, W.L., Leskovec, J., Jurafsky, D., 2016. Diachronic Word Embeddings Reveal Statistical Laws of Semantic Change, in: Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics, ACL 2016, August 7-12, 2016, Berlin, Germany, Volume 1: Long Papers.<br>
Xu, Y., Kemp, C., 2015. A Computational Evaluation of Two Laws of Semantic Change., in: CogSci.<br>
Schlechtweg, Dominik, Stefanie Eckmann, Enrico Santus, Sabine Schulte im Walde, and Daniel Hole, 2017. German in Flux: Detecting Metaphoric Change via Word Entropy. arXiv preprint.<br>
Petersen, A.M., Tenenbaum, J., Havlin, S., Stanley, H.E., 2012. Statistical Laws Governing Fluctuations in Word Use from Word Birth to Word Death. Scientific Reports 2.<br>
Stewart, I., Eisenstein, J., 2018. Making “fetch” happen: The influence of social and linguistic context on nonstandard word growth and decline, in: Proceedings of the 2018 Conference on Empirical Methods in Natural Language Processing. Association for Computational Linguistics, Brussels, Belgium, pp. 4360–4370.<br>
Turney P.D., Mohammad S.M., 2019 The natural selection of words: Finding the features of fitness. PLOS ONE 14(1): e0211512.
</div>

>>>>

<<<<<<< HEAD
---
title: "<span style='line-height:60px; font-size:60px'>Changing communicative need<br>predicts lexical competition<br>and contributes<br>to language change</span></font>"
author: "<font size=6>Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith<br></font><font size=5>Centre for Language Evolution, University of Edinburgh</font>"
date: "<font size=5>RUSE Symposium, Manchester, August 2019</font>"
output:
  xaringan::moon_reader:
    css: img/xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: false
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false
---
class: inverse
# All languages change

@@

<div style="font-size:10pt; line-height:20px">
Karjus, A., Blythe, R.A., Kirby, S., Smith, K., [to appear in Language Dynamics and Change]. Quantifying the dynamics of topical fluctuations in language.<br>
Regier, T., Carstensen, A., Kemp, C., 2016. Languages Support Efficient Communication about the Environment: Words for Snow Revisited. PLOS ONE 11, 1–17.<br>
Gibson, E., Futrell, R., Jara-Ettinger, J., Mahowald, K., Bergen, L., Ratnasingam, S., Gibson, M., Piantadosi, S.T., Conway, B.R., 2017. Color naming across languages reflects color use. Proceedings of the National Academy of Sciences. <br>
Hamilton, W.L., Leskovec, J., Jurafsky, D., 2016. Diachronic Word Embeddings Reveal Statistical Laws of Semantic Change, in: Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics, ACL 2016, August 7-12, 2016, Berlin, Germany, Volume 1: Long Papers.<br>
Xu, Y., Kemp, C., 2015. A Computational Evaluation of Two Laws of Semantic Change., in: CogSci.<br>
Schlechtweg, Dominik, Stefanie Eckmann, Enrico Santus, Sabine Schulte im Walde, and Daniel Hole, 2017. German in Flux: Detecting Metaphoric Change via Word Entropy. arXiv preprint.<br>
Petersen, A.M., Tenenbaum, J., Havlin, S., Stanley, H.E., 2012. Statistical Laws Governing Fluctuations in Word Use from Word Birth to Word Death. Scientific Reports 2.<br>
Stewart, I., Eisenstein, J., 2018. Making “fetch” happen: The influence of social and linguistic context on nonstandard word growth and decline, in: Proceedings of the 2018 Conference on Empirical Methods in Natural Language Processing. Association for Computational Linguistics, Brussels, Belgium, pp. 4360–4370.<br>
Turney P.D., Mohammad S.M., 2019 The natural selection of words: Finding the features of fitness. PLOS ONE 14(1): e0211512.
</div>
=======
---
title: "<span style='line-height:60px; font-size:60px'>Changing communicative need<br>predicts lexical competition<br>and contributes<br>to language change</span></font>"
author: "<font size=6>Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith<br></font><font size=5>Centre for Language Evolution, University of Edinburgh</font>"
date: "<font size=5>RUSE Symposium, Manchester, August 2019</font>"
output:
  xaringan::moon_reader:
    css: img/xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: false
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false
---
class: inverse
# All languages change

<div style="font-size:10pt; line-height:20px">
Karjus, A., Blythe, R.A., Kirby, S., Smith, K., [to appear in Language Dynamics and Change]. Quantifying the dynamics of topical fluctuations in language.<br>
Regier, T., Carstensen, A., Kemp, C., 2016. Languages Support Efficient Communication about the Environment: Words for Snow Revisited. PLOS ONE 11, 1–17.<br>
Gibson, E., Futrell, R., Jara-Ettinger, J., Mahowald, K., Bergen, L., Ratnasingam, S., Gibson, M., Piantadosi, S.T., Conway, B.R., 2017. Color naming across languages reflects color use. Proceedings of the National Academy of Sciences. <br>
Hamilton, W.L., Leskovec, J., Jurafsky, D., 2016. Diachronic Word Embeddings Reveal Statistical Laws of Semantic Change, in: Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics, ACL 2016, August 7-12, 2016, Berlin, Germany, Volume 1: Long Papers.<br>
Xu, Y., Kemp, C., 2015. A Computational Evaluation of Two Laws of Semantic Change., in: CogSci.<br>
Schlechtweg, Dominik, Stefanie Eckmann, Enrico Santus, Sabine Schulte im Walde, and Daniel Hole, 2017. German in Flux: Detecting Metaphoric Change via Word Entropy. arXiv preprint.<br>
Petersen, A.M., Tenenbaum, J., Havlin, S., Stanley, H.E., 2012. Statistical Laws Governing Fluctuations in Word Use from Word Birth to Word Death. Scientific Reports 2.<br>
Stewart, I., Eisenstein, J., 2018. Making “fetch” happen: The influence of social and linguistic context on nonstandard word growth and decline, in: Proceedings of the 2018 Conference on Empirical Methods in Natural Language Processing. Association for Computational Linguistics, Brussels, Belgium, pp. 4360–4370.<br>
Turney P.D., Mohammad S.M., 2019 The natural selection of words: Finding the features of fitness. PLOS ONE 14(1): e0211512.
</div>
>>>>>>> a4a4d625bf79efee1873a824fe28e755e70c6a20
